### 2018-08-07 paper/evaluation.tex
figures!
removed shortcomings in evaluation

@@

Because it sets the top (100\%) and bottom (0\%) values as asymptotes, 
logistic regression does not yield very optimistic success rates at the beginning,
but its midpoint $x_0$ tends to be very accurate even with a low quantity of training samples.

@@

\subsection{Shortcomings} % (fold)
\label{sub:shortcomings}

There are several aspects in \name that can endanger its security or hinder its performance.
First off, we study the RPS and its capacity to provide a random subset of the whole participants list.

>>>>

Overall, we saw 94\% of successful file transfer.

@@

Because it sets the top (100\%) and bottom (0\%) values as asymptotes, 
logistic regression does not yield very optimistic success rates at the beginning,
but its midpoint $x_0$ tends to be very accurate even with a low quantity of training samples.
\commentAL{Yes indeed, very pessimistic, where is our 94\%!? I want to make a CDF also.}

@@

% \subsection{Shortcomings} % (fold)
% \label{sub:shortcomings}

% There are several aspects in \name that can endanger its security or hinder its performance.
% First off, we study the RPS and its capacity to provide a random subset of the whole participants list.
